SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-01-22 scipy-1.0/paper.tex
MAINT: first round of revisions in PR 79.

Python has become so pervasive, there are now domain-specific special issues.
For example, Frontiers in Neuroinformatics has a collection of 25 articles---covering
topics including modeling and simulation, data collection, electrophysiology, visualization,
as well as stimulus generation and presentation---called Python in
neuroscience\footnote{\url{https://www.frontiersin.org/research-topics/8/python-in-neuroscience}}.

In 2012, Perry Greenfield, John Hunter, Jarrod Millman, Travis Oliphant,
and Fernando Pérez founded NumFOCUS\footnote{https://numfocus.org},
 a 501(c)3 public charity whose mission is to
``promote sustainable high-level programming languages, open code development,
and reproducible scientific research.''
While NumFOCUS is language agnostic, many of the early sponsored projects
came from the scientific Python stack.
Today it has over 25 sponsored projects including NumPy, SciPy, IPython, and
Matplotlib.
Among its other projects, NumFOCUS organizes a global network of 
community driven educational programs, meetups, and conferences
called PyData.

@@

The airspeed velocity (asv\cite{asvref}) library enables benchmarking Python packages
over their lifetimes, and the performance of the SciPy code base was monitored
with asv starting in February of 2015 (PR \#4501). In addition to ensuring that
unit tests are passing (see above), confirming that performance generally
remains constant or improves over the commit hash history of the project allows
us to objectively measure that our code base is improving, to empower
scientific applications.

Consider the asv benchmark results shown in Figure~\ref{fig:asvbench}, spanning
roughly nine years of project history. These demonstrate the gradual
performance improvements in a nearest-neighbor search through
\texttt{scipy.spatial.cKDTree.query()}, and can be run using the command:

\texttt{python run.py run -e -s 800 --bench "\textbackslash
btime\_query\textbackslash b" "02de46a546..b3ddb2c"}

>>>>

Python has become so pervasive, there are now domain-specific special issues.
For example, Frontiers in Neuroinformatics has a collection of 25 articles---covering
topics including modeling and simulation, data collection, electrophysiology, visualization,
as well as stimulus generation and presentation---called Python in
neuroscience\cite{python-FIN}.

In 2012, Perry Greenfield, John Hunter, Jarrod Millman, Travis Oliphant,
and Fernando Pérez founded NumFOCUS\cite{numfocus},
 a 501(c)3 public charity whose mission is to
``promote sustainable high-level programming languages, open code development,
and reproducible scientific research.''
While NumFOCUS is language agnostic, many of the early sponsored projects
came from the scientific Python stack.
Today it has over 25 sponsored projects including NumPy, SciPy, IPython, and
Matplotlib.
Among its other projects, NumFOCUS organizes a global network of 
community driven educational programs, meetups, and conferences
called PyData.

@@

The airspeed velocity (asv\cite{asvref}) library enables benchmarking Python packages
over their lifetimes, and the performance of the SciPy code base was monitored
with asv starting in February of 2015 (PR \#4501). In addition to ensuring that
unit tests are passing (see below), confirming that performance generally
remains constant or improves over the commit hash history of the project allows
us to objectively measure that our code base is improving, to empower
scientific applications.

Consider the asv benchmark results shown in Figure~\ref{fig:asvbench}, spanning
roughly nine years of project history. These demonstrate the gradual
performance improvements in a nearest-neighbor search through
\texttt{scipy.spatial.cKDTree.query()}, and can be run using:

\texttt{python run.py run -e -s 800 --bench "\textbackslash
btime\_query\textbackslash b" "02de46a546..b3ddb2c"},

where \texttt{run.py} is a light wrapper script around \texttt{asv}
that is packaged with SciPy.
